\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-19 k-planar.tex
new map graph apps theorem

\begin{thm}
\label{NewMapGraph}
Every $d$-map graph is contained in $H \boxtimes P \boxtimes K_{ d + 3\floor{d/2} -3 }$ for some planar graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{thm}

\cref{NewMapGraph} is an immediate consequence of \cref{d_framed_product_stucture} and the next lemma. Similar results to \cref{MewMapGraphLemma} appear in earlier works \cite{CGP06,BDGGMR,Brandenburg19,Brandenburg20} but we state the precise lemma and provide a proof here for the sake of completeness.

@@

\note{DW}{give a better version of \cref{MapPartition} with $g=0$. }

>>>>

\begin{thm}
\label{MapGraphProduct}
Every $d$-map graph is contained in $H \boxtimes P \boxtimes K_{ d + 3\floor{d/2} -3 }$ for some planar graph $H$ with $\tw(H) \leq 3$ and for some path $P$.
\end{thm}

\cref{MapGraphProduct} is an immediate consequence of \cref{d_framed_product_stucture} and the next lemma. Similar results to \cref{MewMapGraphLemma} appear in earlier works \cite{CGP06,BDGGMR,Brandenburg19,Brandenburg20} but we state the precise lemma and provide a proof here for the sake of completeness.

@@

\cref{MapGraphProduct,qn,p-centered,non-repetitive} imply the following result.

\begin{thm}
\label{PlaneMapApps}
Every $d$-map graph $G$:
	\begin{compactitem}
		\item has queue-number $\qn(G) \leq 24 (d+3\floor{d/2}-3) \,  - \ceil{\tfrac{3}{2} (d+3\floor{d/2}-3)}$.
		\item has $p$-centered chromatic number $\chi_p(G) \leq (d+3\floor{d/2}-3) (p+1)\,  \binom{p+3}{3}$,
		\item has non-repetitive chromatic number $ \pi(G) \leq 256(d+3\floor{d/2}-3) $.
	\end{compactitem}
\end{thm}
